disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Had this problem before. But I think we want to make it clear these are likelihoods (with sim or something). But then you need to distinguish data and estimates.

The different likelihoods correspond to slightly different models ($y_j$ is the repsonse count data):

%
\begin{itemize}
\item {\textbf{Gaussian} ($\sigma_j$ is the dispersion of the polygon data)
\begin{equation} \label{eq:gaussian}
N(y_j/\sum agg_i, rate_j, \sigma_j)
\end{equation}
Here $\sigma_j = \sigma \sqrt{\sum agg_i^2} / \sum agg_i$, where  $\sigma$ is the dispersion of the pixel data (a parameter learnt by the model) }

\item \textbf{Binomial} (For a survey in polygon j, $y_j$ is the number positive and $N_j$ is the number tested),
\begin{equation} \label{eq:binomial}
Binom(y_j, N_j, rate_j)
\end{equation}

\item \textbf{Poisson} (predicts incidence count),
\begin{equation} \label{eq:poisson}
Pois(y_j, cases_j)
\end{equation}

>>>>

The different likelihoods correspond to slightly different models ($y_j$ is the response count data):

%
\begin{itemize}
\item {\textbf{Gaussian} ($\sigma_j$ is the dispersion of the polygon data)
\begin{equation} \label{eq:gaussian}
y_j \sim Normal(count_j/\sum agg_i, rate_j, \sigma_j)
\end{equation}
Here $\sigma_j = \sigma \sqrt{\sum agg_i^2} / \sum agg_i$, where  $\sigma$ is the dispersion of the pixel data (a parameter learnt by the model) }

\item \textbf{Binomial} (For a survey in polygon $j$, $y_j$ is the number positive cases and $N_j$ is the number tested),
\begin{equation} \label{eq:binomial}
y_j \sim Binom(cases_j, N_j, rate_j)
\end{equation}

\item \textbf{Poisson} (predicts incidence count),
\begin{equation} \label{eq:poisson}
y_j \sim Pois(cases_j)
\end{equation}
